Fractional anisotropy as a tracer of cosmic voids

### 2014-11-23 cosmic_voids.tex
Subsection explaining FA.

Once established the FA as the tracer field of cosmic voids, we proceed to
identify individual voids as basins of local minima. For this purpose we
implement a technique developed by \citet{Beucher79} and \citet{Beucher93} 
and widely used in the field of image analysis and mathematical morphology, 
i.e. the \textit{watershed transform algorithm}. This technique has been 
already implemented on void finding schemes by \citet{Platen07} and 
\citet{Neyrinck08} with very interesting results, where individual voids 
are identified as catching basins of local minima of the density field. 
The appeal of this algorithm consists in that is parameter-free and does 
not require any assumption on the shape and morphology of voids. 
Although we use a \textit{cloud-in-cell} (\texttt{CIC}) algorithm on a 
Cartesian mesh for estimating the density and tensor fields, instead of 
the more sophisticated \textit{Delaunay tessellation for field estimator} 
(\texttt{DTFE}) technique \citep{Schaap00}, our implementation of the 
watershed transform should not be significantly affected as we are 
interested in quasi-linear regions where the \texttt{CIC} gives similar 
estimations.

@@

%-------------------------------------------------------------------------
\subsection{Fractional anisotropy as tracer of voids}
\label{subsec:FA_voids}
%-------------------------------------------------------------------------

@@

In left panels of Fig. \ref{fig:FA_field} we calculate the FA for both 
web schemes and the logarithmic density field for a slide of the 
simulation. Some important points can be concluded of this figure.

%.........................................................................
\begin{itemize}
\item Voids display a highly isotropic expanding dynamic at their centres, 
becoming gradually more anisotropic at outer regions.
\item Knots feature with very isotropic collapses. For the Tweb, the FA 
exhibits very narrow distribution around knots whereas for the Vweb, these
distributions are more spread out, thereby indicating strong differences 
between the density and the velocity fields in highly non-linear regions.
\item The filamentary structure of the Cosmic Web is very well traced by
high FA values (black regions), thus indicating very anisotropic dynamics 
for sheets and filaments.
\item The density field poorly traces the Cosmic Web. This is a somehow 
expected result due to the semi-infinite range of the density field, what 
makes more difficult to trace structures.
\end{itemize}
%.........................................................................

Some of these results are consistent with those of \citet{Libeskind13}.
Finally, from Fig. \ref{fig:FA_field} we conclude that the FA, unlike the
density field, displays a non-monotonic behaviour, where low values are 
characteristic of central regions of voids, reaching high values in sheets
and filaments and becoming low again in knots.

For both web schemes, voids are regions where $\lambda_3\leq\lambda_2\leq
\lambda_1\leq\lambda_{th}$. This implies that the outlines of voids
are completely fixed by the relative strength of the $\lambda_1$ 
eigenvalue with respect to the threshold value. Therefore, as we 
increase/decrease the threshold value $\lambda_{th}$, voids expand/diminish
progressively through contours of $\lambda_1$. In Fig. 
\ref{fig:L1_correlations} we calculate the distribution of the FA as well
as of the density field with respect to $\lambda_1$ for both web schemes 
over all cells of the simulation.

From Fig. \ref{fig:L1_correlations} we conclude that the FA is a good
tracer of voids as is perfectly correlated with low values of $\lambda_1$. 
Then, it reaches a maximum value, namely sheets and filaments, for finally
reaching knots, which feature low FA values. This behaviour can be thought 
as a sort of one-dimensional tomography of the Cosmic Web. This 
characteristic allows us to propose an optimal threshold value for both 
web schemes where the FA is maximized. Specifically we propose a value of 
$FA=0.95$, corresponding with a threshold $\lambda_{opt}^T = 0.265$ for
the Tweb and $\lambda_{opt}^V = 0.175$ for the Vweb.  For a threshold 
above these values, voids would span over very anisotropic regions, which 
should correspond to sheets and filaments. A threshold below would imply 
very low volume filling fractions of voids and dominant sheets. Finally 
from the same figure, the density field do not correlate well with 
$\lambda_1$ (as calculated for both web schemes). Moreover, due to its 
monotonic increase, an estimate of a optimal threshold is not as clear as 
for the FA.

@@

@@

  \captionof{figure}{\small Distributions of the fractional anisotropy 
  (left panel) and the density field (right panel) with respect to the 
  eigenvalue $\lambda_1$ for each web scheme (Tweb, red lines. Vweb, 
  blue lines) as calculated over all cells of the grid. Thick central 
  lines correspond with the median and filled regions with the $50\%$ of
  the distribution.}

@@

%.........................................................................
%FIGURE 4: FA and vissual impression
\begin{figure*}
\centering

  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{./figures/cosmicweb_FA_Tweb.pdf}
  \vspace{0.1 cm}
  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{./figures/cosmicweb_FA_Vweb.pdf}
  \vspace{0.1 cm}  
%  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
%  width=0.73\textheight]{./figures/cosmicweb_density.pdf}

  \captionof{figure}{\small Left panels show the visual impression of the 
  Cosmic Web for each web scheme (T-web, upper panels. V-web, middle 
  panels. Density, lower panels). It can be noticed each environment 
  sketched such that voids corresponds to white, sheets to gray, filaments 
  to dark gray and knots to black regions. Right panels show the fractional 
  anisotropy field for the same slide of the simulation and for each web 
  scheme. Black regions correspond to the maxim value, i.e. FA$=1$, while 
  white and light yellow regions to FA$=0$. It is worth noting the 
  degeneration of low values of FA for knots and central regions of voids, 
  thus indicating a high isotropy for both processes. In the same way, high 
  values of FA (FA $\lesssim 1$) are consistent the anisotropic geometry 
  exhibited by filaments and very flat sheets.}

%.........................................................................
%FIGURE 5: volume functions
\begin{flushleft}
\begin{figure*}
\centering

@@

%.........................................................................
%FIGURE 6: Density profile of voids for each defined scheme
\begin{flushleft}
\begin{figure*}
\centering
  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
  width=0.25\textheight]{./figures/voids_density_TwebFAG0.pdf}
  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
  width=0.25\textheight]{./figures/voids_density_VwebFAG0.pdf}
  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
  width=0.25\textheight]{./figures/voids_density_TwebFAG1.pdf}
  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
  width=0.25\textheight]{./figures/voids_density_VwebFAG1.pdf}

@@

%.........................................................................
%FIGURE 7: Velocity profile of voids for each defined scheme
\begin{flushleft}
\begin{figure*}
\centering
  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
  width=0.25\textheight]{./figures/voids_velocity_TwebFAG0.pdf}
  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
  width=0.25\textheight]{./figures/voids_velocity_VwebFAG0.pdf}
  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
  width=0.25\textheight]{./figures/voids_velocity_TwebFAG1.pdf}
  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
  width=0.25\textheight]{./figures/voids_velocity_VwebFAG1.pdf}

@@

>>>>

Once established the FA as the tracer field of cosmic voids, we proceed to
identify individual voids as basins of local minima. For this purpose we
implement a technique developed by \citet{Beucher79} and \citet{Beucher93} 
and widely used in the field of image analysis and mathematical morphology, 
i.e. the \textit{watershed transform algorithm}. This technique has been 
already implemented on void finding schemes by \citet{Platen07} and 
\citet{Neyrinck08} with very interesting results, where individual voids 
are identified as catching basins of local minima of the density field. 
The appeal of this algorithm consists in that is parameter-free and does 
not require any assumption on the shape and morphology of voids. 
Although we use a \textit{cloud-in-cell} (\texttt{CIC}) algorithm on a 
Cartesian mesh for estimating the density and tensor fields, instead of 
the more sophisticated \textit{Delaunay tessellation for field estimator} 
(\texttt{DTFE}) technique \citep{Schaap00}, our implementation of the 
watershed transform should not be significantly affected as we are 
interested in low density regions where the \texttt{CIC} gives similar 
estimations.

@@

%-------------------------------------------------------------------------
\subsection{The fractional anisotropy}
\label{subsec:FA_voids}
%-------------------------------------------------------------------------

@@

In left panels of Fig. \ref{fig:FA_field} we calculate the FA for both 
web schemes over a slide of the simulation. Some important points can be 
concluded from this figure (these results are consistent with those of 
\citet{Libeskind13}).

%.........................................................................
\begin{itemize}
\item Voids display a highly isotropic expanding dynamic at their centres, 
becoming gradually more anisotropic at outer regions.
\item Knots feature with very isotropic collapses. For the Tweb, the FA 
exhibits very narrow distribution around knots. For the Vweb, these
distributions are more spread out, thereby indicating strong differences 
between the density and the velocity fields in highly non-linear regions.
\item The filamentary structure of the Cosmic Web is well traced by high 
FA values (black regions), thus indicating very anisotropic dynamics for 
sheets and filaments.
\item The FA, unlike the density field, displays a non-monotonic behaviour, 
where low values are characteristic of central regions of voids, reaching 
high values in sheets and filaments and becoming low again in knots. 
%\item The density field poorly traces the Cosmic Web. This is a somehow 
%expected result due to the semi-infinite range of the density field, what 
%makes more difficult to trace structures.
\end{itemize}
%.........................................................................

%-------------------------------------------------------------------------
\subsection{Voids using web schemes}
\label{subsec:web_voids}
%-------------------------------------------------------------------------

For both web schemes, voids are regions where $\lambda_3\leq\lambda_2\leq
\lambda_1\leq\lambda_{th}$. This implies that the outlines of voids
are completely fixed by the relative strength of the $\lambda_1$ 
eigenvalue with respect to the threshold value. Therefore, as we 
increase/decrease the threshold value $\lambda_{th}$, voids expand/diminish
progressively through contours of $\lambda_1$. In Fig. 
\ref{fig:L1_correlations} we calculate the distribution of the FA as well
as of the density field with respect to $\lambda_1$ over all cells of the 
grid.

From Fig. \ref{fig:L1_correlations} we conclude that the FA is a good
tracer of voids as is almost perfectly correlated with low values of 
$\lambda_1$. Then, it reaches a maximum value, namely sheets and filaments, 
for finally reaching knots, which feature low FA values. This behaviour can 
be thought as a sort of one-dimensional tomography of the Cosmic Web. This
characteristic allows us to propose an optimal threshold value for both 
web schemes where the FA is maximized. Specifically we propose a value of 
$FA=0.95$, corresponding with a threshold $\lambda_{opt}^T = 0.265$ for
the Tweb and $\lambda_{opt}^V = 0.175$ for the Vweb.  For a threshold 
above these values, voids would span over very anisotropic regions, which 
must correspond to sheets and filaments. A threshold below would imply 
very low volume filling fractions of voids and dominant sheets. Finally, 
the density field do not correlate well with $\lambda_1$ (as calculated 
for both web schemes). Moreover, due to its monotonic increase, an estimate 
of an optimal threshold is not as clear as for the FA.

@@

%.........................................................................
%FIGURE 1: FA and vissual impression
\begin{figure*}
\centering

  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{./figures/cosmicweb_FA_Tweb.pdf}
  \vspace{0.1 cm}
  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{./figures/cosmicweb_FA_Vweb.pdf}

  \captionof{figure}{\small Left panels show the visual impression of the 
  FA field over a slide of the simulation for each web scheme (T-web, upper 
  panels. V-web, middle panels). Black regions correspond with high values, 
  i.e. FA$\approx 1$, while white and light yellow regions to FA$\approx 0$. 
  It is worth noting the degeneration of low values of FA for knots and 
  central regions of voids, thus indicating a high isotropy for both 
  processes. In the same way, high values of FA are consistent with the 
  anisotropic geometry exhibited by filaments and very flat sheets. Middle 
  panels sketch the components of the Cosmic Web using the optimal threshold 
  values. Voids corresponds with white, sheets to gray, filaments to dark 
  gray and knots with black regions. Finally right panels sketch the 
  distribution of the catalogued voids by our method.}

@@

  \captionof{figure}{\small Distributions of the FA (left panel) and the 
  density field (right panel) with respect to the eigenvalue $\lambda_1$ 
  for each web scheme (Tweb, red lines. Vweb, blue lines) as calculated 
  over all cells of the grid. Thick central lines correspond with the median 
  and filled regions with the $50\%$ of the distribution.}

@@

%.........................................................................
%FIGURE 4: volume functions
\begin{flushleft}
\begin{figure*}
\centering

@@

%.........................................................................
%FIGURE 5: Density profile of voids for each defined scheme
\begin{flushleft}
\begin{figure*}
\centering
  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
  width=0.25\textheight]{./figures/voids_density_TwebFAG0.pdf}
  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
  width=0.25\textheight]{./figures/voids_density_VwebFAG0.pdf}
  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
  width=0.25\textheight]{./figures/voids_density_TwebFAG1.pdf}
  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
  width=0.25\textheight]{./figures/voids_density_VwebFAG1.pdf}

@@

%.........................................................................
%FIGURE 6: Velocity profile of voids for each defined scheme
\begin{flushleft}
\begin{figure*}
\centering
  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
  width=0.25\textheight]{./figures/voids_velocity_TwebFAG0.pdf}
  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
  width=0.25\textheight]{./figures/voids_velocity_VwebFAG0.pdf}
  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
  width=0.25\textheight]{./figures/voids_velocity_TwebFAG1.pdf}
  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
  width=0.25\textheight]{./figures/voids_velocity_VwebFAG1.pdf}

@@

%.........................................................................
%%FIGURE 4: density field,impression
%\begin{figure*}
%\centering

%  \includegraphics[trim = 16mm 10mm 295mm 12mm, clip, keepaspectratio=true,
%  width=0.27\textheight]{./figures/cosmicweb_density.pdf}  
%  \captionof{figure}{\small }

%  \label{fig:density_field}
%\end{figure*}
%.........................................................................
